Adaptive Safe Strong Screening for Efficient Lasso-Type Problems Optimization over the Solution Path

### 2021-01-08 main.tex
Edits to 2.4

\subsection{Hybrid safe-strong rules}

The hybrid safe-strong rules (HSSR) \citep{Zeng2021} was proposed to combine SSR with any member of safe rules to take advantage of both. More specifically, it recommended  combining SSR with BEDPP rule, which showed best efficiency in experiments. This algorithm discards features that are discarded by either SSR or BEDPP rule. Then, when doing post-convergence check, it only checks features that are discarded by SSR but not discarded by BEDPP rule, instead of all features that are discarded by SSR.

BEDPP rule is fast because heavy computation only occurs at the first step. SSR only requires heavy computation at the post-convergence check step. Now the set of features that need a post-convergence check is narrowed down by BEDPP rule and thus the cost of the post convergence check is reduced directly. Combining this two rules lead to a hybrid rule that outperforms using any screening rules alone in experiments.

\subsection{Batch screening iterative lasso}

Batch screening iterative lasso (BASIL) \citep{qian2019fast} was proposed to do SSR screening and its following post-convergence check in batches. Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at. First we do the screening for each $\lambda_{k+b}$ value in the batch based on solution at $\lambda_k$ by discarding the $j$-th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$. Then at each $\lambda_{k+b}$ value we solve the lasso problem with only the features that are not discarded. Last at post-convergence check, we search for largest $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that KKT conditions hold for solution at $\lambda_{k+b}$ and accept only the solution from $\lambda_{k+1}$ to $\lambda_{k+b}$. Next, we move to a new batch by replacing the batch head $k$ with $k+b$ and repeat the same procedure again.

The BASIL is most beneficial when the whole $X$ matrix is to large to be fit into the RAM, thus we need to read in a small number of columns $x_j$ from the hard disk at a time. In the post-convergence check for every batch, for each $j$, $x_j$ only needs to be read in once and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$. Moreover, similar to SSR with ordinary post-convergence check, $x_j^Tr(\lambda_{x+b})$ computed at BASIL's post-convergence check step can be reused for screening at next batch.

>>>>

\subsection{Other approaches to screening}

Hybrid safe-strong rules (HSSR) \citep{Zeng2021} were proposed to combine SSR with any safe rule, thereby taking advantage of both. Specifically, they recommended combining SSR with BEDPP rule, which showed the greatest efficiency in experiments. This algorithm discards features that are discarded by either SSR or BEDPP rule. Then, during the post-convergence check, it checks only those features discarded by SSR but not by BEDPP, as the latter can be safely discarded and do not need post-convergence checking. By doing so, the hybrid approach greatly reduces the computational burden of post-convergence KKT checking.  As shown in that paper, hybrid rules combine the advantages of each type of rule, and result in an algorithm that is faster than either strong or safe rules alone.

Batch screening iterative lasso (BASIL) \citep{qian2019fast} was proposed to carry out SSR screening and post-convergence checking in batches. Suppose we have a previous solution $\hat{\beta}(\lambda_k)$ and $r(\lambda_k)$ and the batch of $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$ values we are going to solve at. First, screening is carried out for each $\lambda_{k+b}$ in the batch based $r(\lambda_k$ by discarding the $j$th feature if $|x_j^Tr(\lambda_k)/n|<2\lambda_{k+b}-\lambda_k$. The lasso problem is then solved for $\lam$ values in the batch using only features that are not discarded. Finally, during post-convergence checking, we search for last $k+b$ in the batch $\{k+1,k+2,...,k+B\}$ such that the KKT conditions hold at $\lambda_{k+b}$ and accept only the solutions from $\lambda_{k+1}$ to $\lambda_{k+b}$. Next, we move to a new batch by replacing the batch head $k$ with $k+b$ and repeat the same procedure again.

BASIL is most beneficial when $X$ is to large to be fit into the RAM, as it minimizes the amount of time spent reading from disk. During post-convergence checking, each $x_j$ only needs to be read in once for the entire batch and can be used multiple times for $\{\lambda_{k+1},\lambda_{k+2},...,\lambda_{k+B}\}$. Moreover, similar to SSR, the $x_j^Tr(\lambda_{x+b})$ values computed at BASIL's post-convergence check can be reused for screening at next batch.

\pb{Mention Sure Iterative Screening and why we do not focus on it here; maybe in general, just introduce the idea of stochastic screening}
